Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Added ASD positive diagnosis by sample chunk
Added ADHD positive diagnosis by sample chunk

>>>>

```{r Get ASD positive by sample}

dat.retro_ASD_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(autism_spectrum_disorder_numeric) %>% 
  filter(autism_spectrum_disorder_numeric == 1)

dat.retro_ASD_by_sample <- dat.retro_ASD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("ASD" = n())

```{r Get ADHD positive by sample}

dat.retro_ADHD_by_sample <- dat.retro %>%
  group_by(Sample_plot) %>% 
  select(mhd.attention_deficit_hyperactivity_disorder_numeric) %>% 
  filter(mhd.attention_deficit_hyperactivity_disorder_numeric == 1)

dat.retro_ADHD_by_sample <- dat.retro_ADHD_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise("ADHD" = n())
